% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass{cv-style}     % Add 'print' as an option into the square bracket to remove colours from this template for printing.
                                      % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text
%\setdefaultlanguage{spanish}
%\sethyphenation[variant=spanish]{}{}  % Add words between the {} to avoid them to be cut

\usepackage{graphicx}

\begin{document}

\header{Tom\'as }{Miguez}
\lastupdated

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------
\begin{aside}
%
\section{Contact info}
Buenos Aires, Argentina
tomasmiguez99@gmail.com
+54 9 11 3645 3162
\href{https://www.linkedin.com/in/tom\%C3\%A1s-miguez-a53327241}{LinkedIn}
\href{https://github.com/tomasmiguez}{GitHub}
%
\section{Languages}
Spanish (native),
English (advanced)
%
\section{Programming languages}
Ruby, JavaScript, Python, SQL
%
\section{Frameworks}
Angular, AngularJS, React
%
\section{Other technologies}
Linux, Git
%
\end{aside}
%----------------------------------------------------------------------------------------
% RESUMEN SECTION
%----------------------------------------------------------------------------------------
\vspace{0.2cm}
\section{Intro}
  \vspace{-0.2cm}
  Passionate about programming with a strong interest in functional programming and FOSS.
  Outside of work, I enjoy reading fantasy, playing volleyball, and cycling.
%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{Work experience}
  \vspace{-0.2cm}
\begin{entrylist}
%------------------------------------------------
\entry
  {\scalebox{.8}[1.0]{2021--Present}}
  {Fudo}
  {Ciudad Autónoma de Buenos Aires, Argentina}
  {\jobtitle{Software Engineer}\\
  Implement and maintain solutions throughout the SaaS platform. Participate in
  the design process, collaborating with an interdisciplinary team of skilled
  professionals. Conduct code reviews to uphold standards of maintainability,
  scalability, and extensibility. Refactor legacy code to meet these standards.
  Contribute to the hiring process by interviewing and assessing candidates.

  Key projects I played a significant role in include:
  \begin{itemize}
  \item Developed electronic invoicing solutions for multiple regions,
    integrating with third-party providers and government services, enabling
    the acquisition of clients in new countries.
  \item Integrated our software with existing payment solutions in the region.
  \item Designed and maintained the architecture of both internal and client-facing APIs.
  \item Developed infrastructure for asynchronous job processing.
  \item Created client-facing reporting tools and enhanced back-office analytics systems.
  \item Developed an internal chatbot used by customer support and commercial teams.
  \end{itemize}
  }
%------------------------------------------------
\entry
  {\scalebox{.8}[1.0]{2018--2022}}
  {Philips School}
  {Ciudad Autónoma de Buenos Aires, Argentina}
  {\jobtitle{Teacher}\\
  Taught programming and linear algebra to high school students. Programming was taught
  using C++, and we gave a general overview of what would be an introduction to data structures and
  algorithms at university.}
%------------------------------------------------
\vspace{-0.3cm}
\entry
  {\scalebox{.8}[1.0]{2016--2018}}
  {Philips School}
  {Ciudad Autónoma de Buenos Aires, Argentina}
  {\jobtitle{IT Support}\\
     We were tasked with keeping the institution's hardware in working condition, as
     well as developing web services for students and families as well as faculty and staff.
     Most of the development was done in ASP classic and SQL Server.}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Education}
  \vspace{-0.2cm}
\begin{entrylist}
%------------------------------------------------
\entry
{\scalebox{.8}[1.0]{2018--2025}}
{Licenciatura (Bachelor's \& Master's equivalent) in Computer Science}
{University of Buenos Aires (UBA)}
{}
%------------------------------------------------
\entry
{\scalebox{.8}[1.0]{2018--2020}}
{Licenciatura (Bachelor's \& Master's equivalent) in Mathematics}
{University of Buenos Aires (UBA)}
{Switched focus to Computer Science.}
%------------------------------------------------
\entry
{\scalebox{.8}[1.0]{2012--2017}}
{High school diploma, electromechanical technician}
{Philips School}
{}
%------------------------------------------------
\end{entrylist}
%----------------------------------------------------------------------------------------
% AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Diplomas}
   \vspace{-0.2cm}
\begin{entrylist}
%------------------------------------------------
\entry
{}
{English international exams (C2)}
{}
{Cambridge English: First; Cambridge English: Advanced}
%------------------------------------------------
\end{entrylist}
  \vspace{-0.2cm}
%----------------------------------------------------------------------------------------
\end{document}
